\chapter{Summary and Outlook}
In this thesis, a \ac{daq} for the readout of \acp{wom} was assembled and tested.
It consists of \ac{emusic} boards with \ac{emusic} chips for signal amplification and shaping and \ac{gandalf} modules for digitization.
In the future, it is supposed to be used for the long-term test of the so-called \qq{One Cell Prototype} in Freiburg.

An external clock was developed for the \acp{gandalf} and tested for proper functionality.
This test was done by generating a pure \SI{150}{\mega\hertz} sine waveform with an arbitrary waveform generator and a narrow bandwidth \SI{150}{\mega\hertz} frequency filter.
The peak frequency of the digitized frequency was determined with an \ac{fft} is \SI{149.4(10)}{\mega\hertz} which is in agreement with the theoretical frequency of the sine waveform.
Therefore it can be concluded that the \acp{gandalf} sampling with the correct frequency of \SI{880}{\mega\sample\per\second} and the external clock is working as intended.
Also, the \ac{gandalf} firmware was adjusted to trigger on positive input signals instead of negative pulses.
%Through a bug in the new firmware a surpassing of the maximum datarate of \SI{20}{\mega\byte\per\second} leads to incomplete events which cannot be decoded with the software of the \ac{gandalf}.
%This should not be a problem for the application with the One Cell Prototype since the datarate from firt tests is much lower than the limit.

The most important settings of the \ac{emusic} boards were investigated.
The first of these was the measurement of the input offset voltage used to adjust the overvoltage of the \acp{sipm} on a channel-by-channel level.
%It was found, that the input \ac{dac}, which sets the offset only follows a linear behavior between \SI{100}{\dacu} and \SI{450}{\dacu}.
%In this range the linear behavior measured with the \ac{emusic} board 2 is XXX and for the \ac{emusic} board 6 it is XXX.
%But the input offset differs between the different channels, therefore it is necessary to measure the input offset voltage while adjusting it.
It was found that the input offset voltages of different channels of the same chip differ from each other.
Therefore, the offset voltages need to be adjusted and measured for each channel of each \ac{emusic} board individually. 
For both boards, the input \acp{dac} were set to get approximately \SI{1}{\volt} input offset.


Also, the pole-zero cancellation shaper was tested with different settings.
Therefore measurements with a deactivated pole-zero cancellation shaper were made as a reference.
Also, measurements with eight different settings for the shapers resistor at a constant setting for the shapers capacitor were done to see the effect of the resistor settings.
In order to see the effect of the capacitor, seven measurements with different capacitor settings but the same resistor setting were performed.
The \ac{fwhm} of the signals could be reduced from \SI{113(3)}{\nano\second} down to a minimum of \SI{10.2(6)}{\nano\second}, depending on the pole-zero cancellation settings.
But while the width decreased, the pole-zero cancellation shaper attenuated the signal amplitude from \SI{523(46)}{\milli\volt} down to \SI{143(13)}{\milli\volt}.
In addition to the different pole-zero settings, also the lower attenuation option of the pole-zero cancellation shaper and the high transimpedance mode was tested.

Two dark count measurements were performed, one with and one without the pole-zero cancellation shaper.
For the measurement with the pole-zero cancellation shaper, the resistor setting R=3 and the capacitor setting C=31 were chosen.
In the histogram of the waveform integrals of both measurements, no single photoelectron peaks could be distinguished.
Hence it was not possible to use dark count measurements for calibration.

The \ac{emusic} board was successfully tested at the \ac{desy} testbeam and will be under a long-time performance test starting in the near future.
